Douglas-complex fire smoke and cardiopulmonary morbidity

### 2017-11-29 r_scripts/analysis/oregon_cvd_pulm_results.Rmd
worked on over 65 cvd outcomes; may incorporate in to overall results.
update from upstream/development

Packages used: tidyverse, survival.
```{r setup, echo =F, warning=F, message=F}
library(tidyverse) # general data wrangle
library(survival) # conditional logistic regression

@@

@@

    # fit conditional logistic regression model ----
  mod <- clogit(outcome ~ geo_smk10 + wrf_temp_zip + strata(personkey),
    data = complete_data)

  # odds ratio
  estimates <- round(exp(summary(mod)$coefficient[1,1]), 3) 
  # 95% lower bound
  lower95 <- round(exp((summary(mod)$coefficient[1,1]) -
                                    1.96*(summary(mod)$coefficient[1,3])), 3)
  # 95% upper bound
  upper95 <- round(exp((summary(mod)$coefficient[1,1]) +
                                    1.96*(summary(mod)$coefficient[1,3])), 3)

@@

# ggplot ----
plot <- ggplot(cumulative_results_w_class, 
    aes(x=outcome_names, y = estimate, group=class, color=class)) +
  geom_point() +
  geom_errorbar(aes(ymin=lower95, ymax=upper95), width = 0.2) +
  scale_color_manual(name = "Disease Group", values = c("#4ac29a", "#7303c0"), 
    guide = guide_legend(direction="horizontal", title.position = "top",
                         title.hjust = 0.5)) +
  geom_hline(yintercept = 1, linetype = 2, colour = "#FF0000") +
  theme(panel.background = element_rect(fill = 'white', colour = 'black'),
    legend.position = "bottom",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.text.x = element_text(angle=45, hjust = 1)) +
  ylab(expression("Cumulative odds ratio: 10 ug/m^3 increase smoke PM"[2.5])) +
  xlab(NULL)

@@

### Issues/Concerns (in order of time they popped in my head):
1. File structure needs to be cleaned up. There are way too many subdirectories.
2. Remove r code files that are not useful. There are too many files with similar code inside.
3. Variables in the casecross over datasets raise some questions.
4. Consider a cumulative effect that adds the preceding day and so on, i.e. 0, 0+1, 0+1+2, ...
5. Plots need to have standard labels, ordering, scales, etc.

>>>>

Packages used: idyverse, survival.
```{r setup, echo =F, warning=F, message=F}
library(tidyverse) # general data wrangle
library(survival) # conditional logistic regression

@@

Jeff and Bonne suggest only presenting time-series of 4 counties affected, and send this figure to supplement.

@@

    # fit model with basis ----
  mod <- clogit(outcome ~ geo_smk10 + wrf_temp_zip + strata(personkey),
    data = complete_data)

  # odds ratio
  estimates <- round(exp(summary(mod)$coefficient[1,1]), 3) # sd stands for same day
  # 95% lower bound
  lower95 <- round(exp((summary(mod)$coefficient[1,1]) -
                                    1.96*(summary(mod)$coefficient[1,3])), 3)
  # 95% upper bound
  upper95 <- round(exp((summary(mod)$coefficient[1,1]) +
                                    1.96*(summary(mod)$coefficient[1,3])), 3)

@@

# ggplot ----
plot <- ggplot(cumulative_results_w_class, 
    aes(x=outcome_names, y = estimate, group=class, color=class)) +
  geom_point() +
  geom_errorbar(aes(ymin=lower95, ymax=upper95), width = 0.2) +
  scale_color_manual(name = "Disease Group", values = c("#4ac29a", "#7303c0"), 
    guide = guide_legend(direction="horizontal", title.position = "top",
                         title.hjust = 0.5)) +
  geom_hline(yintercept = 1, linetype = 2, colour = "#FF0000") +
  theme(panel.background = element_rect(fill = 'white', colour = 'black'),
    legend.position = "bottom",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.text.x = element_text(angle=45, hjust = 1)) +
  ylab(expression("Cumulative odds ratio: 10 ug/m^3 increase smoke PM"[2.5])) +
  xlab("Outcomes")

@@

### Issues/Concerns (in order of time they popped in my head):
1. File structure needs to be cleaned up. There are way too many subdirectories.
2. Remove r code files that are not useful. There are too many files with similar code inside.
3. Variables in the casecross over datasets raise some questions.
4. Consider a cumulative effect that adds the preceding day and so on, i.e. 0, 0+1, 0+1+2, ...
5. Plots need to have standard labels, ordering, scales, etc.
6. I'd like to know n-cases and even effect estimates for SABA and asthma in the counties most impacted by smoke.
